Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-10-29 theory.tex
Adding parameter detail to Raetz equation

In the following section, one will describe the different equations and
algorithms used to model the behavior of a symmetric ideal gas centrifuge cascade from the
individual centrifuge property, and to model the centrifuge behavior when fed
with a different feed enrichment than the design one.

@@

As described in \cite{glaser.2008}, the separative power of a single centrifuge
can be express as an analytical solution R\"aetz \cite{raetz.phd} of the
differential equation for the gas centrifuge:

@@

Centrifuge parameters, such as average gas temperature, $T$, peripheral speed,
$v$, height, $h$, diameter, $d$, pressure ratio, $x$, feed flow rate, $F$,
counter-current flow ratio, $L/P$, and efficiency, $e$ have been chosen (Table
\ref{tab:centrifuges}) to match the cascade design describe in
\cite{glaser.2008} and \cite{walker.2017} using P1-type centrifuges.

\begin{table}[htb]
    \centering
    \caption{Summary of the centrifuge parameters.}
    \begin{tabular}{cccccccc}
        \toprule
        $T$[K] & $v$[m/s] & $h$[m] & $d$[m]   & $x$      & $F$[mg/s]  & $L/F$ & $e$  \\
        \midrule
        320    & $320$    & $1.8$  & $0.105$  & $10^{3}$ & $13$       & 2     & 1.0  \\
        \bottomrule
    \end{tabular}
    \label{tab:centrifuges}
\end{table}

>>>>

In the following section, equations and algorithms used to model the behavior of
a symmetric ideal gas centrifuge cascade from the individual centrifuge property
are described. Details will also be provided to model the centrifuge behavior
when fed with a different feed enrichment than the design one.

@@

As described in \cite{glaser.2008}, the separative power of a single centrifuge
can be express as an analytical solution \cite{raetz.phd} of the
differential equation for the gas centrifuge:

@@

In this equation, the parameters of average gas temperature, $T$, peripheral speed,
$v_a$, height, $h$, diameter, $d$, pressure ratio, $x$, feed flow rate, $F$,
counter-current flow ratio, $L/P$, are intrinsic to the centrifuge design.
To match the cascade design describe in \cite{glaser.2008} and \cite{walker.2017},
P1-type centrifuge properties have been chosen (Table \ref{tab:centrifuges}).

\begin{table}[htb]
    \centering
    \caption{Summary of the centrifuge parameters.}
    \begin{tabular}{ccccccc}
        \toprule
        $T$[K] & $v$[m/s] & $h$[m] & $d$[m]   & $x$      & $F$[mg/s]  & $L/F$  \\
        \midrule
        320    & $320$    & $1.8$  & $0.105$  & $10^{3}$ & $13$       & 2   \\
        \bottomrule
    \end{tabular}
    \label{tab:centrifuges}
\end{table}
